Sequence Specific Modeling of \emph{E.~coli} Cell-Free Protein Synthesis

### 2017-05-18 Paper_v1.tex
Fixes??

\subsection{Summary and conclusions}
In this study, we developed a sequence specific constraint based modeling approach to predict the performance of cell-free protein synthesis reactions for a range of proteins.
We showed first principle predictions of the cell-free production of deGFP and CAT, which were in agreement with experimental measurements, under two different promoters.
Here we considered only the P70a and T7 promoters, but we are currently expanding our library of possible promoters.
A library of computational promoters, in combination with the cell-free constraints based approach,
could enable the \emph{de~novo} design of circuits for optimal functionality and performance.
We also developed effective correlation models for the productivity, energy efficiency and carbon yield as a function of protein size.
Simulations of maltose binding protein expression showed good agreement with these correlation models, suggesting the effective correlations could be used to quickly prototype CFPS reactions.
Furthermore, global sensitivity analysis identified oxygen uptake as being instrumental for maintaining a high energy efficiency and carbon yield.
The translation rate was identified as the rate-limiting step for productivity.
The model also suggested that cell-free systems can simultaneously operate aerobically and anaerobically, which can lead to inefficient production and should be addressed to optimize energy efficiency and carbon yield.
In addition, our modeling approach could be expanded with a more detailed description of gene expression that has been utilized in a \emph{E. coli} genome scale model \cite{Brien693}.
We would also like to include post-translation modifications required for proper protein folding and functionality.
In conclusion, sequence specific constraint based modeling offers a novel means to \emph{a~priori} estimate the performance of cell-free synthetic circuits.

>>>>

\subsection{Summary and conclusions}
In this study, we developed a sequence specific constraint based modeling approach to predict the performance of cell-free protein synthesis reactions for a range of proteins.
First principle predictions of the cell-free production of deGFP and CAT were in agreement with experimental measurements, for two different promoters.
Here we considered only the P70a and T7 promoters, but we are currently expanding our library of possible promoters.
A library of computational promoters, in combination with the cell-free constraints based approach,
could enable the \emph{de~novo} design of circuits for optimal functionality and performance.
We also developed effective correlation models for the productivity, energy efficiency and carbon yield as a function of protein size.
Simulations of maltose binding protein expression showed good agreement with these correlation models, suggesting the effective correlations could be used to quickly prototype CFPS reactions.
Furthermore, global sensitivity analysis identified oxygen uptake as being instrumental for maintaining a high energy efficiency and carbon yield.
The translation rate was identified as the rate-limiting step for productivity.
The model also suggested that cell-free systems can simultaneously operate aerobically and anaerobically, which can lead to inefficient production and should be addressed to optimize energy efficiency and carbon yield.
In addition, our modeling approach could be expanded with a more detailed description of gene expression that has been utilized in a \emph{E. coli} genome scale model \cite{Brien693}.
We would also like to include post-translation modifications required for proper protein folding and functionality.
In conclusion, sequence specific constraint based modeling offers a novel means to \emph{a~priori} estimate the performance of cell-free synthetic circuits.
